---
title: "DR Catch Analysis"
author: "Molly Wilson"
date: "10/1/2018"
output: html_document
---

```{r}
library(dplyr)
```


# Import and format catch data

```{r}
cdata <- read.csv("catch_data.csv")

names(cdata) <- names(cdata) %>% make.names() %>% tolower()
names(cdata) <- gsub("number", "n", names(cdata))
names(cdata) <- gsub("weight","wt", names(cdata))
names(cdata) <- gsub("x1st","first", names(cdata))
names(cdata) <- gsub("x2nd","second", names(cdata))
names(cdata) <- gsub("x3rd","third", names(cdata))

cdata <- cdata %>% filter(year!="2012", method!="Trunk") %>%
  select(-c(date,day,video.or.photo,notes)) %>%
  mutate(total.wt=(first.wt+second.wt+third.wt+lionfish.wt+lobster.large.wt+lobster.small.wt+octopus.wt+crab.wt+eel.wt))

# need to adjust other columns to account for number of fishers
```

# Summary calculations
- average total catch per fisherman, by gear type
- average % parrotfish caught, by gear type

```{r}
total_sum <- cdata %>% group_by(method,year) %>% summarise(av.total.wt=sum(total.wt)/sum(n.fishers))

parrot_sum <- cdata %>% group_by(method) %>% summarise(prop.parrot.wt=mean(second.n.parrotfish))
                                                                           #*second.wt+third.n.parrotfish/third.n*third.wt)/total.wt))
```


# Questions for Tyler
1. Have lobster weights already been subtracted from class weights (e.g. are frst/second/third class weights finfish only at this point?)
2. Entries that are missing fish counts: is there a reason for this, or do you think these can still be extrated from videos?