---
title: "DR Catch Analysis"
author: "Molly Wilson"
date: "10/1/2018"
output: html_document
---

```{r}
library(dplyr)
library(ggplot2)
library(tidyr)
```


# Import and format catch data

```{r}
cdata <- read.csv("catch_data.csv")

names(cdata) <- names(cdata) %>% make.names() %>% tolower()
names(cdata) <- gsub("number", "n", names(cdata))
names(cdata) <- gsub("weight","wt", names(cdata))
names(cdata) <- gsub("x1st","first", names(cdata))
names(cdata) <- gsub("x2nd","second", names(cdata))
names(cdata) <- gsub("x3rd","third", names(cdata))

cdata <- cdata %>% filter(year!="2012", method!="Trunk") %>%
  select(-c(date,day,video.or.photo,notes)) %>% 
  mutate_at(vars(first.wt:other.n), funs (./n.fishers)) %>% # divide catch by number of fishers
  uncount(n.fishers) %>% # duplicate rows based on number of fishers
  mutate(
    total.wt.inv=(first.wt+second.wt+third.wt+lionfish.wt+lobster.large.wt+lobster.small.wt+octopus.wt+crab.wt+eel.wt), 
    total.wt=(first.wt+second.wt+third.wt), 
    parrot.wt=(second.n.parrotfish/second.n*second.wt+third.n.parrotfish/third.n*third.wt), 
    parrot.prop=(parrot.wt/total.wt),
    grouper.wt=(first.n.grouper/second.n*first.wt+second.n.grouper/second.n*second.wt+third.n.grouper/third.n*third.wt),
    snapper.wt=(first.n.snapper/second.n*first.wt+second.n.snapper/second.n*second.wt+third.n.snapper/third.n*third.wt),
    grunt.wt=(second.n.grunt/second.n*second.wt+third.n.grunt/third.n*third.wt),
    squirrel.wt=(third.n.squirrelfish/third.n*third.wt)
    )
```

# Summary calculations
- average total catch per fisherman, by gear type
- average % parrotfish caught, by gear type

```{r}
# not explicitly including lobster, etc. in total weights (check with Tyler)
parrot.wt_gear <- cdata %>% group_by(method) %>% summarise(parrotfish=mean(parrot.wt,na.rm=TRUE), grouper=mean(grouper.wt,na.rm=TRUE),snapper=mean(snapper.wt,na.rm=TRUE),grunt=mean(grunt.wt,na.rm=TRUE),squirrel=mean(squirrel.wt,na.rm=TRUE),other=mean(total.wt-parrot.wt-grouper.wt-snapper.wt-grunt.wt-squirrel.wt, na.rm=TRUE)) %>% gather("catch", "weight", 2:7)
```



Average daily catch per fisherman (lbs), proportion parrotfish
```{r}
methodlabs <- c("Spearfishing (compressor)", "Spearfishing (free)", "Other")
ggplot(filter(parrot.wt_gear, method!="Gillnet"), aes(factor(method), weight, fill=factor(catch, levels=c("other","snapper","grunt","squirrel","grouper","parrotfish")))) +
  geom_bar(stat = "identity") +
  labs(y="Daily catch (lbs)",x="",fill="Taxon") +
  scale_fill_brewer(palette="BrBG") +
  scale_x_discrete(labels= methodlabs)
ggsave("dr_catch.png")
```


# Questions for Tyler
1. Have lobster weights already been subtracted from class weights (e.g. are frst/second/third class weights finfish only at this point?)
2. Entries that are missing fish counts: is there a reason for this, or do you think these can still be extrated from videos?
3. Price data (rough)
4. Selectivity data?